Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
fix table alignment
almost there

% i think we do not need to differentiate between semantic web and database integration here, we're saying they're both bad, let's lump them together to keep the argument flowing and not kill our readers
The database integration and Semantic Web \cite{Shadbolt:2006:SWR:1155313.1155373} research communities have primarily focused efforts on purely-automatic approaches to the problem of data integration.  Such approaches typically take the form of either \emph{ontology/schema-level matching}~\cite{euzenat2004api,doan2003learning}, or \emph{direct/instance-level} matching~\cite{suchanek2011paris,castano2006matching}.  We focus on \emph{instance-level} matching, as schemas may not always be available, nor easily accessible to users.

@@

We performed an exploratory sequential mixed-method study to help us design our contribution. For our first pre-study, we sought an updated understanding on the use of multiple information sources in information gathering on the Web. There were two driving questions behind this inquiry; first, were people increasingly relying only on a handful of ``supersites'' (Facebook, Wikipedia), or searching across distributed sources of information?  If the former were true, merely integrating PIM tools with the small number of supersites would provide greater benefit than tackling the substantially more challenging problem of integrating data from arbitrary sources on the Web.  Second, why did people choose a single or multiple sources for information gathering?  If a number of websites were used, why was this preferred over a single source?

@@

%\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported regular use of multiple websites to accomplish tasks, examples of which including: shopping (including food, consumer electronics, hotels and flights), choosing restaurants, job-seeking, selecting a university, seeking recipes, and finding answers to technical problems.  When beginning a task, it was common for participants to use Google to discover several related websites, which would then be used in different ways depending on the task at hand. For shopping-oriented tasks, balancing price, quality and speed of delivery was the main aim.  For product reviews, single sources were not trusted due to possible bias and incomplete feature coverage.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To provide a full coverage of information, websites of different types were used, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.

%\subsubsection{Question 2: Process Used to Organise a Large Social Event}
Participants said they would organise a large social event by first conferring with friends about their ideas, preferences and recommendations.  They selected venues, locations, restaurants and activities through a number of sources: their own prior experience, friends' recommendations, searching Google maps, dedicated reviews sites (such as Yelp for restaurants), and through web search.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web, or organised carpools.  When organising an event, the weather was not that important because they did not trust the accuracy of predictions.  Also, friends' preferences in price and food choices were not seen as a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.

@@

\begin{table*}
\small
\begin{tabular}{p{2.0cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}}
				&				& {\bf average}				& {\bf average }				& 				& {\bf prop name}			& {\bf structural} 			& {\bf model } \\
				& {\bf source}		& {\bf props/record}			& {\bf depth/record}			& {\bf equivalent to}	& {\bf inconsistent}			& {\bf inconsistency} 			& {\bf inconsistency} \\
\hline
social networking	& google+			& 12						& 1.52					& tw:5, li:4, fb:4		& tw:3, li:2, fb:2				& tw:0, li:1, fb:1				& tw:0, li:0, fb:0 \\
(profiles)			& twitter			& 39						& 1.37					& li:4, fb:4 			& li:2, fb:1					& li:0, fb:0					& li:0, fb:0 \\
				& linkedin			& 18						& 2.42					& fb:7			& fb:5					& fb:3					& fb:0 \\
				& facebook		& 22						& 1.5						&				&						&						& \\
\hline
calendars			& google calendar	& 15						& 1.46					& eb:9			& eb:6					& eb:1					& eb:1 \\
(events)			& eventbrite		& 32						& 1.43					&				&						& 						& \\
\hline
retail				& milo			& 5						& 1.2						& z:2, s:3, e:1, a:3	& z:2, s:2, e:1, a:3			& z:0, s:0, e:0, a:2			& z:0, s:0, e:0, a:0 \\
(products)			& zappos			& 6						& 1						& s:2, e:2, a:3		& s:2, e:2, a:2				& s:0, e:0, a:0				& s:0, e:0, a:0 \\
				& shopping.com	& 11						& 3.74					& e:2, a:8			& e:2, a:8					& e:0, a:0					& e:0, a:0 \\
				& etsy			& 31						& 1.13					& a:11			& a:10					& a:1						& a:2 \\
				& amazon			& 108					&						&				& 						&						& \\
\hline
contacts			& google contacts	& 7						& 1.46					& yp:2			& yp:2					& yp: 0					& yp: 0 \\
				& yellowpages		& 25						& 1						&				&						&						& \\
\hline
music			& echonest		& 4						& 1.83					& so:3, r:3, sp:3		& so:3, r:3, sp:3				& so:0, r:0, sp:0				& so:0, r:0, sp:0 \\
(songs/			& soundcloud		& 42						& 2.14					& r:12, sp:7		& r:11, sp:6 				& r:1, sp:1					& r:1, sp:0 \\
tracks)			& rdio			& 27						& 2						& sp: 7			& sp: 6					& sp: 1					& sp: 1 \\
				& spotify			& 10						& 2.44					&				&						&						& \\
\hline
weather			& weatherbug		& 8						& 2						& wu: 5, y: 5		& wu: 5, y: 5				& wu: 5, y: 4				& wu: 0, y: 0 \\
(forecasts)		& wundergound	& 52						& 1.38					& y:12			& y:12					& y:7						& y:3 \\
				& yahoo weather	& 22						& 1.58					&				&						&						& \\
\end{tabular}
\caption{\emph{PS.2 Analysis of Data Feeds} - Structural statistics about data sampled from each API organised by category.  The first column lists the category and type of data record that was examined.  Cols 3 and 4 list the average number of properties per data record, and number of levels from root to leaf. The remaining fields show results from a pairwise analysis of data records from each of the data sources with those of the others in each category; values are prefixed with the first letter(s) of the target schema the row schema was compared against. For example ``Tw:5'' in the 5th column of Google+ row indicates that Facebook and Twitter records had 5 equivalent fields. }\label{tbl:prestudy2}
\end{table*}

@@

Once established, equivalent properties were examined firstly for naming inconsistencies.  Then, ignoring property name, we examined whether the property's values were structurally compatible; if both values consisted of the data type and, if complex, had structurally equivalent subfields, they were considered comparable, otherwise marked \emph{structurally inconsistent}.  Finally, we examined equivalent fields which were incomparable for reasons other than structural or terminological differences.  These \emph{modelling differences} arose from a variety of causes, including, but not limited to: measurement unit inconsistencies, measurement method (e.g., dew point vs relative humidity), differences in scale and granularity, and mismatches in what was being modelled (``offer'' versus ``listing'').\looseness=-1

@@

We also examined the source schemas of data sources for enumerated value types.  There was substantial terminological inconsistency among such value ranges of such types, but also cases where sources had values not represented in the other source's ranges.  For example, the property ``gender''  on Facebook allowed only supported ``male'' and ``female'' for values, while Google+ included a third option,``other''.  Few string representations of enumerated value sets matched across data sources perfectly.

>>>>

% i think we do not need to differentiate between semantic web and database integration here, we're saying they're both bad, let's lump them together to keep the argument flowing and not kill our readers
The database integration and Semantic Web \cite{Shadbolt:2006:SWR:1155313.1155373} research communities have primarily focused efforts on purely-automatic approaches to the problem of data integration.  Such approaches typically take the form of \emph{ontology/schema-level matching}~\cite{euzenat2004api,doan2003learning}, or \emph{direct/instance-level} matching~\cite{suchanek2011paris,castano2006matching}.  We focus on \emph{instance-level} matching, as schemas may not always be available, or easily accessible to users.\looseness=-1

@@

We performed an exploratory sequential mixed-method study to help us design our contribution. For our first pre-study, we sought an updated understanding on the use of multiple information sources in information gathering on the Web. There were two driving questions behind this inquiry: first, were people increasingly relying only on a handful of ``supersites'' (Facebook, Wikipedia), or searching across distributed sources of information?  If the former were true, merely integrating PIM tools with the small number of supersites would provide greater benefit than tackling the more challenging problem of integrating data from arbitrary sources on the Web.  Second, why did people choose a single or multiple sources for information gathering?  If a number of websites were used, why was this preferred over a single source?

@@

%\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported regular use of multiple websites to accomplish tasks, examples of which including: shopping (food, consumer electronics, hotels and flights), choosing restaurants, job-seeking, selecting a university, seeking recipes, and finding answers to technical problems.  When beginning a task, it was common for participants to use Google to discover several related websites, which would then be used in different ways depending on the task at hand. For shopping-oriented tasks, balancing price, quality and speed of delivery was the main aim.  For product reviews, single sources were not trusted due to possible bias and incomplete feature coverage.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To provide a full coverage of information, websites of different types were used, such as manufacturers website for technical details, review aggregators for a range of opinions, and Google maps for location-based decisions.

%\subsubsection{Question 2: Process Used to Organise a Large Social Event}
Participants said they would organise a large social event by first conferring with friends about their ideas, preferences and recommendations.  They selected venues, locations, restaurants and activities through a number of sources: their own prior experience, friends' recommendations, searching Google maps, dedicated reviews sites (such as Yelp for restaurants), and through web search.  People stated that the cost, price and easy to get to locations were the most important factors when choosing a venue.  They considered how to get there and looked up train or bus times on the Web, or organised carpools.  When organising an event, the weather was not that important because they did not trust the accuracy of predictions.  Also, friends' preferences in price and food choices were not seen as a priority; they would try to be inclusive but only if it meant small changes to the plan.  Choosing food and timings were often made on-the-fly, by either with the use of mobile applications or by walking past a location.\looseness=-1

@@

\begin{table*}[htb]
\small
\begin{tabular}{p{2.0cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}  p{1.8cm}}
				&				& {\bf average}				& {\bf average }				& 				& {\bf prop name}			& {\bf structural} 			& {\bf model } \\
				& {\bf source}		& {\bf props/record}			& {\bf depth/record}			& {\bf equivalent to}	& {\bf inconsistent}			& {\bf inconsistency} 			& {\bf inconsistency} \\
\hline
social networking	& google+			& 12						& 1.52					& tw:5, li:4, fb:4		& tw:3, li:2, fb:2				& tw:0, li:1, fb:1				& tw:0, li:0, fb:0 \\
(profiles)			& twitter			& 39						& 1.37					& li:4, fb:4 			& li:2, fb:1					& li:0, fb:0					& li:0, fb:0 \\
				& linkedin			& 18						& 2.42					& fb:7			& fb:5					& fb:3					& fb:0 \\
				& facebook		& 22						& 1.5						&				&						&						& \\
\hline
calendars			& google calendar	& 15						& 1.46					& eb:9			& eb:6					& eb:1					& eb:1 \\
(events)			& eventbrite		& 32						& 1.43					&				&						& 						& \\
\hline
retail				& milo			& 5						& 1.2						& z:2, s:3, e:1, a:3	& z:2, s:2, e:1, a:3			& z:0, s:0, e:0, a:2			& z:0, s:0, e:0, a:0 \\
(products)			& zappos			& 6						& 1						& s:2, e:2, a:3		& s:2, e:2, a:2				& s:0, e:0, a:0				& s:0, e:0, a:0 \\
				& shopping.com	& 11						& 3.74					& e:2, a:8			& e:2, a:8					& e:0, a:0					& e:0, a:0 \\
				& etsy			& 31						& 1.13					& a:11			& a:10					& a:1						& a:2 \\
				& amazon			& 108					&						&				& 						&						& \\
\hline
contacts			& google contacts	& 7						& 1.46					& yp:2			& yp:2					& yp: 0					& yp: 0 \\
				& yellowpages		& 25						& 1						&				&						&						& \\
\hline
music			& echonest		& 4						& 1.83					& so:3, r:3, sp:3		& so:3, r:3, sp:3				& so:0, r:0, sp:0				& so:0, r:0, sp:0 \\
(songs/			& soundcloud		& 42						& 2.14					& r:12, sp:7		& r:11, sp:6 				& r:1, sp:1					& r:1, sp:0 \\
tracks)			& rdio			& 27						& 2						& sp: 7			& sp: 6					& sp: 1					& sp: 1 \\
				& spotify			& 10						& 2.44					&				&						&						& \\
\hline
weather			& weatherbug		& 8						& 2						& wu: 5, y: 5		& wu: 5, y: 5				& wu: 5, y: 4				& wu: 0, y: 0 \\
(forecasts)		& wundergound	& 52						& 1.38					& y:12			& y:12					& y:7						& y:3 \\
				& yahoo weather	& 22						& 1.58					&				&						&						& \\
\end{tabular}
\caption{\emph{PS.2 Analysis of Data Feeds} - Structural statistics about data sampled from each API organised by category.  The first column lists the category and type of data record that was examined.  Cols 3 and 4 list the average number of properties per data record, and number of levels from root to leaf. The remaining fields show results from a pairwise analysis of data records from each of the data sources with those of the others in each category; values are prefixed with the first letter(s) of the target schema the row schema was compared against. For example ``Tw:5'' in the 5th column of Google+ row indicates that Facebook and Twitter records had 5 equivalent fields. }\label{tbl:prestudy2}
\end{table*}

@@

Once established, equivalent properties were examined firstly for naming inconsistencies.  Then, ignoring property name, we examined whether the property's values were structurally compatible; if both values consisted of the data type and, if complex, had structurally equivalent subfields, they were considered comparable, otherwise marked \emph{structurally inconsistent}.  Finally, we examined equivalent fields which were incomparable for reasons other than structural or terminological differences.  These \emph{modelling differences} arose from a variety of causes, including: unit inconsistencies, measurement method (e.g., dew point vs relative humidity), differences in scale and granularity, and mismatches in what was being modelled (``offer'' versus ``listing'').\looseness=-1

@@

We also examined the source schemas of data sources for enumerated value types.  There was substantial terminological inconsistency among such value ranges of such types, but also cases where sources had values not represented in the other source's ranges.  For example, ``gender''  on Facebook allowed only ``male'' and ``female'' for values, while Google+ included a third option,``other''.  Few string representations of enumerated value sets matched across data sources perfectly.
